```{r, echo=F, message=F}
source(here::here("scripts/setup.R"))
```

# Exploratory Data Analysis (EDA)

To proceed to the Exploratory Data Analysis (EDA), we use the **quanteda package**.

## Cloud of Words plot

The Cloud of Words plot is possible representation used to visualize term frequencies. Nevertheless, this vizualition is more graphic than informative, this is why we decided to start our EDA with. 

The size and the position (centered) are propotional to the frequency.

[Improve plot: use different colors]

```{r cloud of words for corpus plot, echo=F, message=F, warning=F}

CoW_cp <- textplot_wordcloud(data.dfm)

CoW_cp 

```

This plot shows that the most frequent terms in the corpus seems to be women, female, male, datum, etc...


## Global frequencies


To assess a bit more seriously the frequency of the terms, we compute the global frequencies and show the results in the plot below. The following visualization plots the 10 most frequent terms in the whole corpus. As we supposed previously with the cloud of words, the plot indicates that the term *woman* is the most frequent term overall, followed by female, datum, male and, find. The frequency difference between those words are so slight that it was hard to distinguish their rank. In addition we can see that the term "data" has been changed by lemmatization to "datum". 

[Improve plot: layout/color/add title/add subtitle/caption with source]

```{r TF-IDF plot, echo=F, message=F, warning=F}

# Generates counts and document frequencies summaries of the feature of the document-feature matrix "data.dfm"
data.freq <- textstat_frequency(data.dfm) 

#Plot the results 
tf_plot <- data.freq  %>% 
              top_n(10, frequency) %>%                    # selects the top 10 rows by frequency values
              ggplot(aes(x = reorder(feature, frequency), # orders terms by frequency values
                         y = frequency)) + 
              geom_bar(stat = "identity", fill = "dodgerblue3", alpha = 0.5) + # generates a barplot
              coord_flip() +                              # flips the coordinates
              xlab("Frequency") + 
              ylab("Term") +
              theme_minimal() +
              ggtitle("Top 10 global frequencies")

tf_plot

```
To deep dive in those frequencies, we display the terms frequency table below which resumes numerically the information (???).  The *feature* column indicates lemmatized tokens, *frequency* returns the number of time the term is found in the corpus, the *rank* sorts the terms by decreasing frequencies, the *docfreq* indicates the document frequency which is the number of documents in which the token is found. There is an important point to make here, "woman" appears 1594 times in the corpus and it is not a specific term as it appears in all the documents. Moreover *woman* appears four times more than the second most frequent term *female* in the corpus and this huge difference could hide some insights.


```{r term frequency, echo = FALSE, message = FALSE}
kbl(head(data.freq[,1:4], 10), align = c('c', 'c', 'c', 'c', 'c'), #originally the data.freq has a column named group but as it is not relevant for us we select only the 3 first columns
    caption = "Term frequencies") %>% 
  kable_styling(bootstrap_options = c("striped", "hover"), 
                full_width = NULL)  
```
## Term Frequency against Document Frequency 

Now let's have a global graphical view on the frequency of a term relative to its document frequency (i.e. number of documents in which a term is found), indicating whether a word is specific to a document or not. As seen previously, we see that *women* is not document-specific since it is the most frequent term over all chapters of the book and that it is found in all of them. On the contrary, the words *trial* and *tax* are less frequent and also less frequent in documents making them more document-specific. 
 
For all the reasons mentionned until here, we decided to remove "woman" for the rest of our analysis.
[Improve plot]

```{r TF vs DF, echo=F, message=F, warning=F}

data.freq %>% 
 ggplot(aes(x = log(docfreq), 
  y = log(frequency))) +
 geom_text(aes(label = feature), 
      position = position_jitter(), 
      size=3) + 
 labs(title = "TF versus DF (log-log)",
   subtitle = "",
   x = "Document log-frequency",
   y = "Term log-frequency",
  caption = "source: Invisible Women.pdf") +
  theme_minimal()




```

```{r second cleaning, echo = FALSE, message = FALSE}
# second cleaning without "woman"
data.tk3 <- data.tk2 %>% tokens_remove("woman")

# Creates a second document-feature matrix
data.dfm2 <- dfm(data.tk3) 

# generate second second doc frequency
data.freq2 <- textstat_frequency(data.dfm2)  

# Generate a second weighted document-feature matrix by tf-idf
data.tfidf2 <- dfm_tfidf(data.dfm2)
```


## Term-Frequency by Document 

The plot below shows the same information, ten most frequent [frequencies] terms, but by chapters of the book. Here, we show the ten most frequent [frequencies] terms associated with their chapter (i.e. document). We see that the term *woman* is the most associated with chapters 11, 10 and 3 which are respectively, *Yentl Syndrome*, *The Drugs Don't Work* and *The Long Friday*. 

Regarding the term *female*, even though it is the second most frequent term in the book, it seems to be more specific to chapter 14 *Women's Rights are Human Rights* since we only find it in this particular chapter [is this right?]. 

[Improve plot: color, layout, title, caption with source, can we change text1 by the name of the chapter ?]

-> MAYBE REMOVE WOMEN like in the Harry Potter example and explain why we remove it
-> I removed all terms like women, female etc... just for this plot, otherwise it is meaningless so we need to change the whole interpretation.  

-> justifier pq on fait pas l'autre plot avec les freq par doc. 

--------------------------------------------------------------------------------------------------------------------------
The plot below shows the same information but with a little twist, ten most frequent terms along with the book chapters in which they appear.

We see that the term *woman* is the most associated with chapters 11, 10 and 3 which are respectively, *Yentl Syndrome*, *The Drugs Don't Work* and *The Long Friday*. 

Regarding the term *female*, even though it is the second most frequent term in the book, it seems to be more specific to chapter 14 *Women's Rights are Human Rights* since we only find it in this particular chapter [is this right?]. 

[Improve plot: color, layout, title, caption with source, can we change text1 by the name of the chapter ?]

-> MAYBE REMOVE WOMEN like in the Harry Potter example and explain why we remove it
-> I removed all terms like women, female etc... just for this plot, otherwise it is meaningless so we need to change the whole interpretation.  

-> justifier pq on fait pas l'autre plot avec les freq par doc. 


```{r cloud of words by document plot, echo=F, message=F, warning=F}

nowoman.10 <- data.dfm2 %>% 
           tidy() %>%  
           #group_by(term) %>% !!!!
  # creates a tibble 
           top_n(10, count) %>%       # selects the top 10 rows by count   
           #ungroup() %>% !!!! 
           ggplot(aes(x = reorder(term, count), 
                      y = count)) +   
           geom_col(fill = "dodgerblue3", alpha = 0.5) + 
           coord_flip() + 
           xlab("Term") +
           ylab("Frequency") +
           facet_wrap(~ document, 
                      ncol = 2) +
           theme_minimal() +
           ggtitle("Top 10 frequencies along with documents")

nowoman.10


#---> Il y a un soucis ça plot pas les 10 termes les plus fréquents au travers de tous les docs mais juste les 10 fréquences les plus hautes par doc... Pas sûre d'être claire
```




